---
title: "Code Execution and Display Features"
author: "Quarto Review Team"
format:
  html:
    toc: true
    code-fold: true
    code-line-numbers: true
execute:
  daemon: false
---

# Code Execution and Display

This document demonstrates code execution, display options, and language support in Quarto.

## Python Code {#sec-python}

### Basic Python Code Block

```{python}
#| label: fig-python-basic
#| fig-cap: "Python code execution output"

import numpy as np
import matplotlib.pyplot as plt

# Generate sample data
x = np.linspace(0, 10, 100)
y = np.sin(x)

# Create plot
plt.figure(figsize=(10, 5))
plt.plot(x, y, 'b-', linewidth=2)
plt.scatter(x[::10], y[::10], color='red', s=100)
plt.title('Sine Wave')
plt.xlabel('X')
plt.ylabel('Y')
plt.grid(True, alpha=0.3)
plt.tight_layout()
plt.show()
```

### Python with Code Annotations

```{python}
#| code-annotations: below

data = {              # <1>
    'name': ['Alice', 'Bob', 'Charlie'],
    'age': [25, 30, 35],
    'city': ['NYC', 'LA', 'Chicago']
}

for person in data['name']:  # <2>
    print(f'Hello, {person}!')
```

1. Create a dictionary with sample data
2. Iterate through each person in the data

### Python with Code Folding

```{python}
#| code-fold: show
#| code-summary: "Show the calculation"

# Calculate statistics
numbers = [1, 2, 3, 4, 5, 6, 7, 8, 9, 10]
mean = sum(numbers) / len(numbers)
variance = sum((x - mean) ** 2 for x in numbers) / len(numbers)
std_dev = variance ** 0.5

print(f"Mean: {mean}")
print(f"Variance: {variance}")
print(f"Standard Deviation: {std_dev}")
```

## R Code

### R Code Block

```{r}
#| label: fig-r-plot
#| fig-cap: "R ggplot2 example"

# Install and load ggplot2
library(ggplot2)

# Create sample data
df <- data.frame(
  x = 1:10,
  y = rnorm(10, mean = 5, sd = 2),
  group = rep(c("A", "B"), each = 5)
)

# Create plot
ggplot(df, aes(x = x, y = y, color = group)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal() +
  labs(title = "Random Data with Groups",
       x = "X Axis",
       y = "Y Axis")
```

### R with Output Options

```{r}
#| eval: true
#| echo: true
#| output: true

# R code that shows both code and output
x <- c(1, 2, 3, 4, 5)
y <- x^2

data.frame(x = x, y = y)
```

## Julia Code

::: {.callout-note}
Julia code execution via JuliaCall is disabled in this environment due to compatibility issues in containers. The code examples below show syntax but are not executed.
:::

### Julia Code Block

```julia
using Plots, Random

# Set random seed for reproducibility
Random.seed!(42)

# Generate sample data
x = range(0, 2π, length=100)
y1 = sin.(x)
y2 = cos.(x)

# Create plot
plot(x, [y1 y2],
     label=["sin(x)" "cos(x)"],
     title="Trigonometric Functions",
     xlabel="x",
     ylabel="y",
     legend=:topright)
```

### Julia Computation

```julia
# Simple Julia computation
function fibonacci(n)
    if n <= 1
        return n
    else
        return fibonacci(n-1) + fibonacci(n-2)
    end
end

# Calculate Fibonacci numbers
fib_sequence = [fibonacci(i) for i in 0:10]
println("Fibonacci sequence: ", fib_sequence)
```

## Observable JavaScript

### Observable JS Reactive Code

```{ojs}
// Define a slider input
viewof x = Inputs.range([0, 10], {step: 0.1, label: "x"})

// Define a function
y = Math.sin(x)

// Display results
html`<p>x = ${x.toFixed(2)}, y = ${y.toFixed(4)}</p>`
```

## Code Display Options

### Code with Line Numbers

```{python}
#| code-line-numbers: true

def greet(name):
    """A simple greeting function."""
    message = f"Hello, {name}!"
    return message

result = greet("World")
print(result)
```

### Code with Filename Display

```{python}
#| filename: "example.py"

#!/usr/bin/env python3
"""
This is a Python script with a filename displayed.
"""

def main():
    print("Hello from a named file!")

if __name__ == "__main__":
    main()
```

### Code Without Code Folding

```{python}
#| code-fold: false

# This code is always visible, not folded
print("This code will not be folded")
```

### Code with Copy Button

Code blocks automatically include a copy button on hover. Try hovering over any code block!

```javascript
// JavaScript example with copy button
const greeting = "Hello, Quarto!";
console.log(greeting);
```

## Code Execution Options

### Eval: False (Show Code Only)

```{python}
#| eval: false

# This code is shown but not executed
result = very_expensive_computation()
print(result)
```

### Echo: False (Show Output Only)

```{python}
#| echo: false

# This code runs but isn't shown
import json
data = {"key": "value", "number": 42}
print(json.dumps(data, indent=2))
```

### Hidden Code Block

```{python}
#| include: false

# This code runs silently in the background
x = 10
y = 20
z = x + y
```

## Inline Code Execution

Python inline code: `{python} 2 + 2`

R inline code: `{r} nrow(mtcars)`

## Code with Warnings and Errors

```{python}
#| warning: true

import warnings
warnings.warn("This is a demonstration warning")

# Code continues after warning
print("Code still runs after warning")
```

## Summary

This document demonstrates Quarto's comprehensive code execution and display features including:

- Code in multiple languages (Python, R, Julia, Observable JS)
- Execution control (eval, echo, include)
- Display options (code folding, line numbers, annotations)
- Interactive elements and visualizations
- Code copy buttons and filenames
